Executive Constraints and Civil Conflict Onset

### 2020-02-12 paper.Rmd
Switch post file paths to use new csv extracts

```{r  fig.cap = "\\label{fig:fpars} Measurement Model Parameter Estimates"}
load("./posteriors/full_model/input.RData")
fa <- read_post("./posteriors/full_model/fa_posteriors.csv.gz")

@@

```{r fig.cap = "\\label{fig:fa-line} Posterior shrinkage for \\textit{v2juncind}"}
err <- read_post("posteriors/full_model/err_posteriors.csv.gz")

@@

```{r reg, fig.height = 3}
reg <- read_post("posteriors/full_model/reg_posteriors.csv.gz")

@@

```{r fig.height = 2, fig.cap = "\\label{fig:phat} Density plot for predicted probabilities"}
p_hat <- extract(reg, "p_hat")

@@

# TODO: this is killing our compile times
all_betas <- mclapply(models, function(f) {
    load(file.path("posteriors", f, "input.RData"))
    beta <- file.path("posteriors", f, "reg_posteriors.csv.gz") %>%
        read_post %>%
        extract("beta")

>>>>

```{r  fig.cap = "\\label{fig:fpars} Measurement Model Parameter Estimates"}
load("./posteriors/full_model/input.RData")
fa <- read_post("./posteriors/full_model/fa_posteriors.csv")

@@

```{r fig.cap = "\\label{fig:fa-line} Posterior shrinkage for \\textit{v2juncind}"}
err <- read_post("posteriors/full_model/err_posteriors.csv")

@@

```{r reg, fig.height = 3}
reg <- read_post("posteriors/full_model/reg_posteriors.csv")

@@

```{r fig.height = 2, fig.cap = "\\label{fig:phat} Density plot for predicted probabilities"}
extra <- read_post("posteriors/full_model/extra_posteriors.csv")
p_hat <- extract(extra, "p_hat")

@@

# TODO: this is killing our compile times
all_betas <- mclapply(models, function(f) {
    load(file.path("posteriors", f, "input.RData"))
    beta <- file.path("posteriors", f, "reg_posteriors.csv") %>%
        read_post %>%
        extract("beta")
